### 2016-06-06 R/ITHIM.Rmd
Added a little road injury code to ITHIM.Rmd

```{r plot4, echo = FALSE, fig.height = 12}
D<-melt(comparitiveRisk$AF)
names(D)<- c("age","sex","AF","disease")
p <- ggplot(D, aes(age,AF)) + geom_bar(aes(fill=sex), stat = "identity") + facet_grid( disease ~ .) + coord_cartesian(ylim = c(0, 0.1))
p
```
# Code Graveyard

>>>>

```{r plot4, echo = FALSE, fig.height = 12}
D<-melt(comparitiveRisk$AF)
names(D)<- c("age","sex","AF","disease")
p <- ggplot(D, aes(age,AF)) + geom_bar(aes(fill=sex), stat = "identity") + facet_grid( disease ~ .) + coord_cartesian(ylim = c(0, 0.1))
p
```
### Road Injury Array
```{r road}
baselineInjuries <- array(dim=c(6,7,3,2))
injury <- c("fatal","serious")
road <- c("minor road","major road","motorway")
vehicle <- c("walk","cycle","bus","car","HGV","mbike")
dimnames(baselineInjuries) <- list(vehicle,c(vehicle,"NOV"),road,injury)

```
# Code Graveyard
